%          ╭──────────────────────────────────────────────────────────╮
%          │                       Frontmatter                        │
%          ╰──────────────────────────────────────────────────────────╯
\begin{frontmatter}

% ── Title ─────────────────────────────────────────────────────────────
\title{An optimal volumetric constraint ratio with implementation using mixed FE-Meshfree formulation}
% \title{A Mixed FEM-Meshfree Formulation with Optimal Constraint Ratio for the Divergence--locking Problems}

% ── Author ────────────────────────────────────────────────────────────
\author[1]{Wu Junchao\corref{cor1}}
\ead{jcwu@hqu.edu.cn}
\author[2]{Chu Yingjie}
\author[1]{Xu Yangtao}
\author[2]{Wang Dongdong}

\affiliation[1]{
    organization={
        Key Laboratory for Intelligent Infrastructure and Monitoring of Fujian Province,
        College of Civil Engineering,
        Huaqiao University
    }, 
    city={Xiamen},
    state={Fujian}, 
    postcode={361021},
    country={China},
}

\cortext[cor1]{Corresponding author}

% ── Abstract ──────────────────────────────────────────────────────────
\begin{abstract}
% Formulations for incompressible materials often suffer from volumetric locking, leading to reduced accuracy and oscillatory displacement and pressure solutions.
% A well-chosen constraint ratio can mitigate this issue, but traditional approaches lack a theoretical foundation based on the inf-sup (or LBB) condition, which is essential for the stability of mixed formulations.
% This paper introduces a novel optimal constraint ratio derived from the inf-sup condition to address volumetric locking.
% The inf-sup test, a numerical tool for verifying the inf-sup condition, is reaffirmed as equivalent to inf--sup condition through a variational approach.
% By incorporating a complete polynomial space whose dimension matches the number of displacement degrees of freedom (DOFs),
% a new inf-sup value estimator is developed, explicitly considering the constraint ratio.
% For a given number of displacement DOFs, ensuring that the pressure DOFs remain below a stabilized number falls within the optimal constraint ratio range can satisfy the inf-sup condition.
% To implement of optimal constraint ratio, a mixed finite element and meshfree formulation is proposed,
% where displacements are discretized using traditional finite element approximations, and pressures are approximated via the reproducing kernel meshfree method.
% Leveraging the globally smooth reproducing kernel shape functions,
% the constraint ratio can be flexibly adjusted to meet the inf-sup condition without the limit of element.
% For computational efficiency and ease of implementation, pressure nodes are placed on selected displacement nodes to maintain the optimal constraint ratio.
% Inf-sup tests and a series of 2D and 3D elasticity examples validate the proposed constraint ratio, demonstrating its effectiveness in eliminating volumetric locking and enhancing the performance of mixed finite element and meshfree formulations.

Formulations for incompressible materials often suffer from volumetric locking, leading to reduced accuracy and oscillatory displacement and pressure solutions.
A well-chosen constraint ratio can mitigate this issue, but traditional approaches lack a theoretical foundation based on the inf-sup (or LBB) condition, which is essential for the stability of mixed formulations.
This paper introduces a novel optimal constraint ratio derived from the inf-sup condition to address volumetric locking.
The inf-sup test, a numerical tool for verifying the inf-sup condition, is reaffirmed as equivalent to the inf-sup condition through a variational approach.
By incorporating a complete polynomial space whose dimension matches the number of displacement degrees of freedom (DOFs), a new inf-sup value estimator is developed, explicitly considering the constraint ratio.
For a given number of displacement DOFs, ensuring that the pressure DOFs remain below a stabilized number falls within the optimal constraint ratio range can satisfy the inf-sup condition.
To implement the optimal constraint ratio, a mixed finite element and meshfree formulation is proposed, where displacements are discretized using traditional finite element approximations, and pressures are approximated via the reproducing kernel meshfree method.
Leveraging the globally smooth reproducing kernel shape functions, the constraint ratio can be flexibly adjusted to meet the inf-sup condition without the limit of element.
For computational efficiency and ease of implementation, pressure nodes are placed on selected displacement nodes to maintain the optimal constraint ratio.
Inf-sup tests and a series of 2D and 3D elasticity examples validate the proposed constraint ratio, demonstrating its effectiveness in eliminating volumetric locking and enhancing the performance of mixed finite element and meshfree formulations.
\end{abstract}

% ── Keywords ──────────────────────────────────────────────────────────
\begin{keyword}
    Optimal constraint ratio
    \sep
    Inf--sup condition estimator
    \sep
    Volumetric locking
    \sep
    Mixd formulation
    \sep
    Reproducing kernel meshfree approximation
\end{keyword}

\end{frontmatter}
